Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-25 analysis/paper/paper.Rmd
Add 'egg' and 'tidyr' to the libs used for plot construction

packages <- c(
  "extrafont",
  "officer",
  "dplyr",
  "ggpubr",
  "ggplot2",
  "janitor",
  "here",
  "flextable",
  "tidyr",
  "DiagrammeR",
  "DiagrammeRsvg",
  "rsvg",
  "ggplot2",
  "bayesplot",
  "patchwork"
)

>>>>

packages <- c(
  "extrafont",
  "egg",
  "officer",
  "dplyr",
  "ggpubr",
  "ggplot2",
  "janitor",
  "here",
  "flextable",
  "tidyr",
  "DiagrammeR",
  "DiagrammeRsvg",
  "rsvg",
  "ggplot2",
  "bayesplot",
  "tidyr",
  "patchwork"
)
